What to simulate? Inferring the direction for mental rotation

### 2014-01-30 man/cogsci-2014/cogsci-2014.tex
Misc edits

@@

@@

\title{Modeling mental simulation: a computational analysis of mental rotation}

@@

\TODO{need a figure with an example similarity curve, and example
  stimuli}

\TODO{fix title}

@@

One of our most astonishing cognitive feats is the ability to
envision, manipulate, and plan with objects -- all without actually
perceiving them. This capacity for ``mental simulation'' has been
widely studied and has sparked intense debate about the underlying
representation of mental images \cite<e.g.,>{Kosslyn:2009tj,
  Pylyshyn:2002vk}. Despite this vast literature, there have been
surprisingly few computational models of mental imagery.

@@

@@

We randomly generated 20 shapes of 5 or 6 vertices (e.g., $\Xa$ in
Figure \ref{fig:stimuli}). For each shape, we computed 20 ``same'' and
20 ``flipped'' stimuli pairs, with $\theta$ spaced at $20^\prime$
increments between 0 and 360 (with 0 and 180 degree rotations repeated
twice, in order to gather an equal number of responses for each angle
between 0 and 180). ``Same'' pairs were created by rotating $\Xa$ by
$\theta$; ``flipped'' pairs first reflected $\Xa$ across the $y$-axis,
then rotated by $\theta$.

@@

\begin{figure*}[t]
  \begin{center}
    \includegraphics[width=\textwidth]{../../figures/D/model-traces.pdf}
    \caption{\textbf{Model traces.} \TODO{} \TODO{put pictures of the
        stimuli here}}
    \label{fig:model-traces}
  \end{center}
\end{figure*}

@@

\section{Acknowledgments}

This research was supported by ONR MURI grant number N00014-13-1-0341,
and a Berkeley Fellowship awarded to JBH.

\bibliographystyle{apacite}

\setlength{\bibleftmargin}{.125in}
\setlength{\bibindent}{-\bibleftmargin}

\bibliography{references}

>>>>

%% For better looking math (but it takes up more space):
% \AtBeginDocument{\RequirePackage{lmodern, times}}

@@

\addtolength{\abovecaptionskip}{-0.25cm}
\addtolength{\belowcaptionskip}{-0.2cm}
\addtolength{\textfloatsep}{-2mm}	% space below "Figure 1: ..."

@@

\title{What to simulate? Inferring the direction for mental rotation}

@@

@@

One of our most astonishing cognitive feats is the ability to
envision, manipulate, and plan with objects -- all without actually
perceiving them. This capacity for ``mental simulation'' has been
widely studied and has sparked intense debate about the underlying
representation of mental images \cite<e.g.,>{Kosslyn:2009tj,
  Pylyshyn:2002vk}. But this debate hasn't addressed one of the most
fundamental questions about mental simulation: how people decide what
they should simulate.

@@

\begin{figure*}[t]
  \begin{center}
    \includegraphics[width=\textwidth]{../../figures/D/model-traces.pdf}
    \caption{\textbf{Model traces.} \TODO{}}
    \label{fig:model-traces}
  \end{center}
\end{figure*}

@@

We randomly generated 20 shapes of 5 or 6 vertices (e.g., the stimuli
in Fig.~\ref{fig:model-traces}). For each shape, we computed 20
``same'' and 20 ``flipped'' stimuli pairs, with $\theta$ spaced at
$20^\prime$ increments between 0 and 360 (with 0 and 180 degree
rotations repeated twice, in order to gather an equal number of
responses for each angle between 0 and 180). ``Same'' pairs were
created by rotating $\Xa$ by $\theta$; ``flipped'' pairs first
reflected $\Xa$ across the $y$-axis, then rotated by $\theta$.

@@

@@

%% TODO: Uncomment this for final version:

% \section{Acknowledgments}
% {\small This research was supported by ONR MURI grant number
% N00014-13-1-0341, and a Berkeley Fellowship awarded to JBH. }

\bibliographystyle{apacite}
\renewcommand{\bibliographytypesize}{\small}
\setlength{\bibleftmargin}{.125in}
\setlength{\bibindent}{-\bibleftmargin}
\bibliography{references}
